FinalManuscript_DISCS_UG

### 2019-03-07 parts/05_conclusions.tex
Fixed typo
fix ch5

\chapter{CONCLUSIONS}
In this study, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like DGK.

@@

Efforts are ongoing with regard to the facial recognition tests. Our own implementation of the privacy-preserving  eigenfaces by Erkin, et al. does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.

>>>>

\chapter{CONCLUSIONS}
In this study, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain.

@@

Efforts are ongoing with regard to the facial recognition tests. Our own implementation of the privacy-preserving eigenfaces by Erkin, et al. does not yet use the DGK cryptosystem for secure integer comparison in the match finding step.
